Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2018-10-21 pkg/disttree/inst/draft/draft.Rnw
adaption to new results of Rain_distribution and further revisions based on reviews
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2346 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 7ebcc9e62debed3abf93f2f926af1ebb44bc0415

\item \emph{Distributional forest:} All 80~predictor variables are
  considered for learning a forest of 100 trees. Subsampling is employed 
  for each tree using a third of the predictors
  in each split of the tree (\code{mtry}). Parameters are estimated by
  adaptive local likelihood based on the forest weights as described
  in Section~\ref{sec:methods}. 
  \hlc{As stopping criteria the minimal number of observations to perform a split} 
  (\code{minsplit}) \hlc{is set to $50$, the minimal number of observations in a 
  terminal node} (\code{minbucket})\hlc{is set to $20$ and the significance level 
  for variable selection} (\code{alpha}) \hlc{is kept at the default value $1$.}
  % stopping criteria:
  % forest_minsplit = 50, forest_minbucket = 20, forest_mincrit = 0

@@

\subsubsection{Distributional specifications}
%% choice of distribution mit Verweis auf Supplement distributions
\hlc{Choosing an adequate distributional family is a crucial step and forms
the basis required to build a well fitting model. Therefore, this
decision should be made thoughtfully. 
In the presented application we applied a Gaussian distribution left-censored 
at zero as this has proven to be a well working choice in
earlier literature} \citep{Stauffer+Mayr+Messner:2017}. 
\hlc{To test for robustness against distributional misspecifation 
different distributional assumptions have been considered as well. 
In Supplement 1 (Different Response Distributions) the exact
same evaluations as in} Section~\ref{sec:all} \hlc{are carried out for 15
observation stations, once employing a Gaussian hurdle model and once
with a logistic distribution left-censored at zero in order to account
for heavier tails. Under both assumptions the obtained results 
are similar to those presented in the paper applying a Gaussian distribution
left-censored at zero. However, comparing the two censored distributions,
at many stations the models perform not as well under the logistic distribution 
as under the Gaussian distribution. The hurdle model leads to slight improvements 
in some settings, but this comes with more variability (especially for EMOS and the 
boosted GAMLSS).
Altogether, the distributional forest has proven to be very robust against
distributional misspecifications.}

@@

The smaller the $p$-value corresponding to the standardized test 
statistic $c(t_{l},\mu_{l},\Sigma_{l})$ is the stronger the discrepancy 
from the assumption of independence between the scores and the split 
variable $Z_l$.
%
After Bonferroni-adjusting the $p$-values it has to be assessed whether
any of the resulting $p$-values is beneath the selected significance level. 
If so, the partitioning variable $Z_{l^\ast}$ with the lowest $p$-value 
is chosen as splitting variable. \hlc{Otherwise no further split is made 
in this node as the stopping criterion of no $p$-values being below the 
significance level is fulfilled.}

>>>>

\item \emph{Distributional forest:} All 80~predictor variables are
  considered for learning a forest of 100 trees. Subsampling is employed 
  for each tree using a third of the predictors
  in each split of the tree (\code{mtry}). Parameters are estimated by
  adaptive local likelihood based on the forest weights as described
  in Section~\ref{sec:methods}. 
  \hlc{As stopping criteria the minimal number of observations to perform a split} 
  (\code{minsplit}) \hlc{is set to $50$, the minimal number of observations in a 
  terminal node} (\code{minbucket}) \hlc{is set to $20$ and the significance level 
  for variable selection} (\code{alpha}) \hlc{is kept at the default value $1$ such 
  that no early-stopping (sometimes also refered to as ``pre-pruning'') is applied
  based on results of the statistical tests.}
  % stopping criteria:
  % forest_minsplit = 50, forest_minbucket = 20, forest_mincrit = 0

@@

\subsubsection{Distributional specifications}
%% choice of distribution mit Verweis auf Supplement distributions
\hlc{Choosing an adequate distributional family is a crucial step and forms
the basis required to build a well fitting model. Therefore, this
decision should be made thoughtfully. 
In the presented application we applied a Gaussian distribution left-censored 
at zero as this has proven to be a well working choice in
earlier literature} \citep{Stauffer+Mayr+Messner:2017}. 
\hlc{To test for robustness against distributional misspecifation 
different distributional assumptions have been considered as well. 
In Supplement 1 (Different Response Distributions) the exact
same evaluations as in} Section~\ref{sec:all} \hlc{are carried out for 15
observation stations, once employing a Gaussian hurdle model and once
with a logistic distribution left-censored at zero in order to account
for heavier tails. Under both assumptions the obtained results 
are similar to those presented in the paper applying a Gaussian distribution
left-censored at zero. In some settings the hurdle model leads to slight 
improvements, but this comes with more variability (especially for EMOS and the 
boosted GAMLSS). For the boosted GAMLSS the left-censored logistic distribution
shows slightly better results, however, only within a range of less than $2\%$
and not for all stations. Altogether, the distributional forest has proven to be 
very robust against distributional misspecifications.

Alternatively, a distribution including an addidtional parameter capturing skewness
\citep{Scheuerer+Hamill:2015, Baran+Nemoda:2016} could be applied. For example, 
in transformation forests} \citep{Hothorn+Zeileis:2017} \hlc{a very flexible 
five-parametric distribution family is employed such that skewness can be modeled 
explicitly.
Evaluating further distributions might be of interest but this would go beyond the
scope of this manuscript.
}

@@

The smaller the $p$-value corresponding to the standardized test 
statistic $c(t_{l},\mu_{l},\Sigma_{l})$ is the stronger the discrepancy 
from the assumption of independence between the scores and the split 
variable $Z_l$.
%
After Bonferroni-adjusting the $p$-values it has to be assessed whether
any of the resulting $p$-values is beneath the selected significance level. 
If so, the partitioning variable $Z_{l^\ast}$ with the lowest $p$-value 
is chosen as splitting variable. \hlc{Otherwise no further split is made 
in this node as the stopping criterion of no $p$-values being below the 
significance level is fulfilled. This type of early-stopping in building
a tree is sometimes also referred to as ``pre-pruning''. For forest models
pre-pruning is often switched off by setting the significance level to $1$.}
